---
title       : Prediction with Galton's Data
subtitle    : Linear Regression Model
author      : RongChen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]      # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Galton'Data
There are two questions we trying to answer:


1.To try to find a parsimonious, easily described relationship between parent and children's heights.

2.To use the parents' heights to predict children's heights.

```{r,echo=FALSE}    
library(UsingR); data(galton)
par(mfrow=c(1,2), mar = c(4, 4, 2, 1),oma = c(15, 0, 0, 0))
hist(galton$child,col="blue",breaks=100,xlab = "child",main="")
hist(galton$parent,col="blue",breaks=100,xlab = "parent",main="")
```

--- .class #id 

## The solution of the best fit model
Let $Y_i$ be the $i_th$ child's height and $X_i$ be the $i_th$ parents' heights.

Consider finding the best line: $Child's Height = \beta_0+ Parent's Height*\beta_1$

Our goal is to minimize the least squares: $$\sum_{i=1}^n \{Y_i-(\beta_0+\beta_1X_i)\}^2$$

R can help us find the best fit model
```{r}  
fit<-lm(child~parent,data=galton)
```


--- .class #id 

## Visualizing the best fit line 

```{r,echo=FALSE}  
freqData <-as.data.frame(table(galton$parent, galton$child))
names(freqData) <- c("child", "parent", "freq")
plot(as.numeric(as.vector(freqData$parent)),
     as.numeric(as.vector(freqData$child)),
     pch = 21, col = "black", bg = "lightblue",
     cex = .15 * freqData$freq,
     xlab = "parent",ylab = "child")
abline(coef(fit)[1],coef(fit)[2],lwd = 3)
mse <- mean((galton$child-galton$parent*coef(fit)[2]-coef(fit)[1])^2)
title(paste("intercept =",round(coef(fit)[1],3),
            "slope=",round(coef(fit)[2],3),
            "mse = ", round(mse, 3)))
```


--- .class #id 

##  Prediction and My Shiny Application


Finally, Here is my application on Rstudio's shiny server
https://april.shinyapps.io/prediction/

Everyone can use it to understand how linear regression model works and predicte childrens' heights via parents' heights.The function I use to predict is as follows:
```{r} 
bestfit<-function(parent_height) {
    fit<-lm(child~parent,data=galton)
    coef(fit)[1]+coef(fit)[2]*parent_height
}
```





